Who introduced this bug? \\ It may not have been caused by the previous commit!

### 2016-01-30 paperMSR.tex
añadidas mas cosas... i need info

\documentclass{sig-alternate-05-2015}
\usepackage{url}
\usepackage{epsfig}
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{float}           % H para posicionar figuras
\usepackage{booktabs}
\begin{document}

@@

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Gema Rodr\'iguez\\
       \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Madrid, Spain}\\
       \email{gerope@libresoft.es}
% 2nd. author
\alignauthor
Jesus M. Gonz\'alez-Barahona\\
      \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Madrid, Spain}\\
       \email{jgb@gsyc.es}
% 3rd. author
\alignauthor Gregorio Robles\\
       \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Madrid, Spain}\\
       \email{grex@gsyc.urjc.es}
\and  % use '\and' if you need 'another row' of author names
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{29 January 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

This paper tries to shed some light on this topic, by analyzing the relationship of bug fixes with their previous commits. To this end, we conducted an observational study on bug reports, their fixes, and their corresponding previous commits for the OpenStack project. Our results show that the assumption that bugs have been introduced in the previous commit does not hold for a large fraction of the bugs analyzed. FIXME: maybe something more here
\end{abstract}

@@

When a failure is found in the behavior of a software, the developers try to fix it locating and modifying the source code line(s) that are reponsible for the wrong behaviour in the source code. It seems reasonable to assume that the previous modification of this line or these lines are the cause of the bug; this previous modification is \textit{the previous commit}. But in fact, to find when and where a bug was introduced in the source code is not a trivial task. This has largely been ignored, mainly because the data related to the origin of a bug is embedded in the evolution of the software~\cite{sinha2010buginnings}. FIXME: clarificar la frase anterior... no ha quedado muy claro.

@@

Based on anecdotal evidence like the one presented in Figures~\ref{fig:3} and Figure~\ref{fig:4}, we argue that in projects that are continuously evolving, with an ample developer community, code that before was correct could be buggy at some time. So, changes in other parts
of the code may induce wrong behavior (bugs) in places that were correct in the past. This happens often in situations like changes to the API. In the moment the code ws written, it was correct and the woftware worked fine. Additions of new features or enhancements to the API had as a side effect that the formerly correct code presents a wrong behavior, making the software fail. But in such cases, the source of the error cannot be FIXME assigned to a change performed in the previous commit, as in that moment it referred to a different API.

FIXME: poner esto bien

The goal of this paper is to find if the cause of the bug can be FIXME assigned to the previous commit, understanding that at the time when the previous commit is introduced

not all times the code analyzed was so easy as the code showed in figures \ref{fig:1} and \ref{fig:3}. So the principal aim of this paper to find the responsible of the bug is to know if the previous commits contained buggy code at the moment in which were added/modified or, another change in the software, related to the update of the software and its evolution, caused the bug.

@@

FIXME: rephrase RQs

@@

FIXME: This last paragraph should be clarified, and more on papers using the SZZ algorithm! Maybe we should state how many papers in total exist based or using SZZ in Google Scholar.

@@

FIXME: maybe talk about my paper with dmg and ahmed, where bugs could be found elsewhere~\cite{german2009change}. There the talk is precisely about those bugs whose origina are elsewhere. Title of the paper: \emph{Change impact graphs: Determining the impact of prior codechanges}

@@

\begin{itemize}
  \item The title of the issue report
  \item The description of the issue report
  \item The description of the fix commit
  \item The changes to the source code, as sometimes neither the descriptions nor the comments by developers in the Launchpad and Gerrit of each ticket, clarified the underlying ticket. FIXME: what comments?
\end{itemize}

@@

\begin{enumerate}
    \item When the ticket title described the program as not working as expected, our criteria indicated that it was a bug report. 
    \item When the title described optimization, deletion of a dead code or the implementation of new characteristics, we agreed not to classify it as a bug report because there is no failure. 
    \item When the ticket title described that updates were required, the ticket is a bug report. We consider all tickets that require updating as bug reports, because updating a software hints to the software not operating as expected. 
    \item When only test files are affected in a ticket, we classified it as not being a bug report. Test files in a ticket were not be analyzed, as we consider they are not a core part of the software and are used as a testing method to determine whether the code is fit for use. When the bug exclusively lies in a test file, the ticket was not considered as bug report because the software still works as expected, only test fails. FIXME: no se repiten las frases?
\end{enumerate}

@@

The next part is focused on analyzing the previous commit exclusively in the \textit{Bug Report} group to identify which line contained the bug and why the software failed, keeping in mind the context of the project. For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added,inserted or modified in the previous commit. This way, we can be sure that we are looking the correct change, because some times although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, is a false positive where the previous commit didn't cause the bug. FIXME: aclarar este parrafo!

@@

This analysis takes into account that the bug could have been inserted in many lines belong to many differnt previous commits, but in fact, not all of them could cause the bug. Could happen that these previous commit copied lines from its previous commits or modified the comments and added blank spaces. Thus, the cause could be found in a single previous commit, in many or even in none. FIXME: repasar este parrafo

@@

As can be seen in Table~\ref{tab:responsability}, in 152 cases the previous commits have been considered the cause of the bug, whereas 114 times they were not the cause. We were unable to identify the cause of the bug in 42 cases, and discarded 40 more because they ere false positives such as blank lines, changes in comments or even a change in the version of the file. FIXME: explicar que es eso de noise!, Con Noise me referia a los falsos positivos que puede haber en los commits previos, las líneas copiadas de otros commits o lineas en blanco, comentarios ...

@@

FIXME: Debería hablar sobre los siguientes puntos:
\begin{enumerate}
 \item No todos los casos son tan claros como los mostrados en los ejemplos....
 \item Casuistica del common juidment
 \item Hemos sido conservadores
 \item Hemos utilizado la herramienta porque es un proceso complicado
\end{enumerate}

@@

\begin{itemize}
    \item The word \textit{bug} is continuously mentioned in the description and commit of a ticket even when we found it is not an error. This could lead to the incorrect classification during the reviewing process.
    \item Some tickets are not explicitly described, which could increase the percentage of \textit{Undecided}. This is especially true if the reviewers are not from OpenStack.
    \item OpenStack is a special project put down a constant evolution due to their active community of developers. Maybe, in other projects with less commits per year the statistics about the responsibility of previous commit change.
\end{itemize}
FIXME: Anñadir un link con la web en la que pondré todos los datos y scripts utilizados para los datos.

>>>>

\newif\ifdraft
\drafttrue
%\draftfalse

\documentclass{sig-alternate-05-2015}
\usepackage{url}
\usepackage{epsfig}
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{float}           % H para posicionar figuras
\usepackage{booktabs}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xspace}

\input{macros}

\begin{document}

@@

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Gema Rodr\'iguez\\
       \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Madrid, Spain}\\
       \email{gerope@libresoft.es}
% 2nd. author
\alignauthor
Jes\'us M. Gonz\'alez-Barahona\\
      \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Madrid, Spain}\\
       \email{jgb@gsyc.es}
% 3rd. author
\alignauthor Gregorio Robles\\
       \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Madrid, Spain}\\
       \email{grex@gsyc.urjc.es}
\and  % use '\and' if you need 'another row' of author names
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{29 January 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

This paper tries to shed some light on this topic, by analyzing the relationship of bug fixes with their previous commits. To this end, we conducted an observational study on bug reports, their fixes, and their corresponding previous commits for the OpenStack project. Our results show that the assumption that bugs have been introduced in the previous commit does not hold for a large fraction of the bugs analyzed. \grex{maybe we could say something more here}.
\end{abstract}

@@

When a failure is found in the behavior of a software, the developers try to fix it locating and modifying the source code line(s) that are reponsible for the wrong behaviour in the source code. It seems reasonable to assume that the previous modification of this line or these lines are the cause of the bug; this previous modification is \textit{the previous commit}. But in fact, to find when and where a bug was introduced in the source code is not a trivial task. This has largely been ignored, mainly because the data related to the origin of a bug is embedded in the evolution of the software~\cite{sinha2010buginnings}. \grex{clarificar la frase anterior... no ha quedado muy claro.}

@@

Based on anecdotal evidence like the one presented in Figures~\ref{fig:3} and Figure~\ref{fig:4}, we argue that in projects that are continuously evolving, with an ample developer community, code that before was correct could be buggy at some time. So, changes in other parts
of the code may induce wrong behavior (bugs) in places that were correct in the past. This happens often in situations like changes to the API. In the moment the code ws written, it was correct and the woftware worked fine. Additions of new features or enhancements to the API had as a side effect that the formerly correct code presents a wrong behavior, making the software fail. But in such cases, the source of the error cannot be \grex{assigned} to a change performed in the previous commit, as in that moment it referred to a different API.

\grex{poner el siguiente parrafo bien}

The goal of this paper is to find if the cause of the bug can be \grex{assigned} to the previous commit, understanding that at the time when the previous commit is introduced

not all times the code analyzed was so easy as the code showed in Figures~\ref{fig:1} and~\ref{fig:3}. So the principal aim of this paper to find the responsible of the bug is to know if the previous commits contained buggy code at the moment in which were added/modified or, another change in the software, related to the update of the software and its evolution, caused the bug.

@@

\grex{rephrase RQs}

@@

\grex{This last paragraph should be clarified, and more on papers using the SZZ algorithm! Maybe we should state how many papers in total exist based or using SZZ in Google Scholar.}

@@

\grex{maybe talk about my paper with dmg and ahmed, where bugs could be found elsewhere~\cite{german2009change}. There the talk is precisely about those bugs whose origina are elsewhere. Title of the paper: \emph{Change impact graphs: Determining the impact of prior codechanges}}

@@

\begin{itemize}
  \item The title of the issue report
  \item The description of the issue report
  \item The description of the fix commit
  \item The changes to the source code, as sometimes neither the descriptions nor the comments by developers in the Launchpad and Gerrit of each ticket, clarified the underlying ticket. \grex{what comments?}
\end{itemize}

@@

\begin{enumerate}
    \item When the ticket title described the program as not working as expected, our criteria indicated that it was a bug report. 
    \item When the title described optimization, deletion of a dead code or the implementation of new characteristics, we agreed not to classify it as a bug report because there is no failure. 
    \item When the ticket title described that updates were required, the ticket is a bug report. We consider all tickets that require updating as bug reports, because updating a software hints to the software not operating as expected. 
    \item When only test files are affected in a ticket, we classified it as not being a bug report. Test files in a ticket were not be analyzed, as we consider they are not a core part of the software and are used as a testing method to determine whether the code is fit for use. When the bug exclusively lies in a test file, the ticket was not considered as bug report because the software still works as expected, only test fails. \grex{no se repiten las frases?}
\end{enumerate}

@@

The next part is focused on analyzing the previous commit exclusively in the \textit{Bug Report} group to identify which line contained the bug and why the software failed, keeping in mind the context of the project. For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added,inserted or modified in the previous commit. This way, we can be sure that we are looking the correct change, because some times although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, is a false positive where the previous commit didn't cause the bug. \grex{aclarar este parrafo!}

@@

This analysis takes into account that the bug could have been inserted in many lines belong to many differnt previous commits, but in fact, not all of them could cause the bug. It could have happened that in the previous commit lines had been copied from further previous commits, or comments may have been modified, or blank spaces/lines have been added. Thus, the cause could be found in a single previous commit, in many or even in none. \grex{repasar este parrafo}

@@

As can be seen in Table~\ref{tab:responsability}, in 152 cases the previous commits have been considered the cause of the bug, whereas 114 times they were not the cause. We were unable to identify the cause of the bug in 42 cases, and discarded 40 more because they ere false positives such as blank lines, changes in comments or even a change in the version of the file. \grex{explicar que es eso de noise!} \gema{Con Noise me referia a los falsos positivos que puede haber en los commits previos, las lineas copiadas de otros commits o lineas en blanco, comentarios ...}

@@

\gema{Deberia hablar sobre los siguientes puntos:} \grex{Puedes elaborar un poco mas cada punto, aunque sea en castellano?}
\begin{enumerate}
 \item No todos los casos son tan claros como los mostrados en los ejemplos....
 \item Casuistica del common juidment
 \item Hemos sido conservadores
 \item Hemos utilizado la herramienta porque es un proceso complicado
\end{enumerate}

@@

\begin{itemize}
    \item The word \textit{bug} is continuously mentioned in the description and commit of a ticket even when we found it is not an error. This could lead to the incorrect classification during the reviewing process.
    \item Some tickets are not explicitly described, which could increase the percentage of \textit{Undecided}. This is especially true if the reviewers are not from OpenStack.
    \item OpenStack is a special project put down a constant evolution due to their active community of developers. Maybe, in other projects with less commits per year the statistics about the responsibility of previous commit change.
\end{itemize}

\gema{Incluir un link con la web en la que pondré todos los datos y scripts utilizados para los datos.}
